pema application

### 2022-11-10 paper/manuscript.Rmd
Update

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low.
  [The present study introduces Bayesian Regularized Meta-Analysis (BRMA),
  which uses regularizing (LASSO or horseshoe) priors to shrink small
  regression coefficients towards zero]{#lassoabstract}, thereby selecting relevant
  moderators from a larger number of candidates.
  This approach is suitable when heterogeneity is suspected,
  but it is not known which moderators most strongly inﬂuence the
  observed effect size.
  We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art random effects meta-analysis using REML   (RMA).
  Results indicated that BRMA compared favorably to RMA on three metrics:
  predictive performance (a measure of generalizability),
  the ability to reject irrelevant moderators,
  and the ability to recover population parameters with
  low bias.
  BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explore between-studies heterogeneity
  in meta-analysis.

@@

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This work used the *random forest* algorithm; a non-parametric approach that largely ignores irrelevant moderators.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly for a readership that is accustomed to linear models,
where the effect of each predictor is described by a single parameter.
An alternative method for variable selection that can be used in linear models is *regularization*:
shrinking model parameters towards zero, such that irrelevant moderators are eliminated.
The present paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
The algorithm is implemented in the function `brma()` in the R-package `pema`.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->

>>>>

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low.
  [The present study introduces Bayesian Regularized Meta-Analysis (BRMA),
  which uses regularizing (LASSO or horseshoe) priors to shrink small
  regression coefficients towards zero]{#lassoabstract}, thereby selecting relevant
  moderators from a larger number of candidates.
  This approach is suitable when heterogeneity is suspected,
  but it is not known which moderators most strongly inﬂuence the
  observed effect size.
  We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art random effects meta-analysis using REML   (RMA).
  Results indicated that BRMA compared favorably to RMA on three metrics:
  predictive performance (a measure of generalizability),
  the ability to reject irrelevant moderators,
  and the ability to recover population parameters with
  low bias.
  BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explore between-studies heterogeneity
  in meta-analysis.
  The method is implemented in the R-package 
  `pema` (penalized meta-analysis) and in the free open source statistical software package JASP.

@@

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This work used the *random forest* algorithm; a non-parametric approach that largely ignores irrelevant moderators.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly for a readership that is accustomed to linear models,
where the effect of each predictor is described by a single parameter.
An alternative method for variable selection that can be used in linear models is *regularization*:
shrinking model parameters towards zero, such that irrelevant moderators are eliminated.
The present paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability mass to near-zero values,
which keeps small regression coefficients close to zero, resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->
